Non-linear Spatio-temporal modelling using the Integro-Difference Equation

### 2010-07-08 ltx/second_order_framework/second_order_manuscript.tex
minor correction to second order mo0del derivation and added discritization

\begin{equation*}

@@

d\tilde{v}(\mathbf r,t)+2\zeta\tilde{v}(\mathbf r,t)dt+\zeta^2v_tdt=&g'(\mathbf r,t)dt+dW(\mathbf r,t)

@@

@@

 d\begin{bmatrix} v_t(\mathbf r ,t) \\ \tilde{v}_t(\mathbf r ,t)\end{bmatrix}=\begin{bmatrix}0 & 1 \\ \zeta^2 & 2\zeta \end{bmatrix}\begin{bmatrix} v_t(\mathbf r ,t) \\ \tilde{v}_t(\mathbf r ,t)\end{bmatrix}dt+\begin{bmatrix}0 \\ g'(\mathbf r, t)\end{bmatrix}dt+\begin{bmatrix}0 \\ 1 \end{bmatrix}dW(\mathbf r,t)

>>>>

\begin{equation*}\label{eq:SecondOrderInitialValueProblem}

@@

d\tilde{v}(\mathbf r,t)+2\zeta\tilde{v}(\mathbf r,t)dt+\zeta^2v(\mathbf r,t)dt=&g'(\mathbf r,t)dt+dW(\mathbf r,t)

@@

\begin{equation}\label{eq:SecondOrderSDEMatrix}
 d\begin{bmatrix} v_t(\mathbf r ,t) \\ \tilde{v}_t(\mathbf r ,t)\end{bmatrix}=\begin{bmatrix}0 & 1 \\ -\zeta^2 & -2\zeta \end{bmatrix}\begin{bmatrix} v_t(\mathbf r ,t) \\ \tilde{v}_t(\mathbf r ,t)\end{bmatrix}dt+\begin{bmatrix}0 \\ g'(\mathbf r, t)\end{bmatrix}dt+\begin{bmatrix}0 \\ 1 \end{bmatrix}dW(\mathbf r,t)

@@

 \begin{bmatrix} v_{t+T_s}(\mathbf r)-v_t(\mathbf r) \\ \tilde{v}_{t+T_s}(\mathbf r)-\tilde{v}_t(\mathbf r)\end{bmatrix}=T_s\begin{bmatrix}0 & 1 \\ -\zeta^2 & -2\zeta \end{bmatrix}\begin{bmatrix} v_t(\mathbf r)\\ \tilde{v}_t(\mathbf r)\end{bmatrix}+T_s\begin{bmatrix}0 \\ g'(\mathbf r, t)\end{bmatrix}+\begin{bmatrix}0 \\ 1 \end{bmatrix}(W_{t+T_s}(\mathbf r)-W_t(\mathbf r))
